Optical characterization of gaps in directly bonded Si compound optics using infrared spectroscopy

### 2015-01-21 AO_bondedSi.tex
convert VS20-21 image from bitmap to pdf, fix bug in subsection heading

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.3\columnwidth]{figs/VS2021_IR_image.bmp}}
\caption{
\label{figVS2021_IR_image}
IR image of part VS20-21. Three rectangular mesh areas are apparent (Table \ref{tabPatternFills}).  The coarsest mesh, C, shows substructure, while the medium and fine meshes are indistinguishable at the low resolution of the image.  The three dark spots are gaps at the inferface of the direct bonded Si samples.}
\end{figure}

@@

\subsectio{Inferring axial extent of gaps from noisy transmission spectra}
We infer the axial extent of the gaps with correlated measurement uncertainties using Gaussian Processes.

>>>>

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.4\columnwidth]{figs/VS2021_IR_image.pdf}}
\caption{
\label{figVS2021_IR_image}
IR image of part VS20-21. Three rectangular mesh areas are apparent (Table \ref{tabPatternFills}).  The coarsest mesh, C, shows substructure, while the medium and fine meshes are indistinguishable at the low resolution of the image.  The three dark spots are gaps at the inferface of the direct bonded Si samples.}
\end{figure}

@@

\subsection{Inferring axial extent of gaps from noisy transmission spectra}
We infer the axial extent of the gaps with correlated measurement uncertainties using Gaussian Processes.
